Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-25 paper/paper.tex
observe-bete-binomial -> observe-beta-bernoulli

In addition to distributions, Anglican provides \textit{random processes},
which define sequences of random variables that are not independent and
identically distributed. Random processes are similar to the so called
`exchangeable random primitives' in Church \cite{GMR+08} and
Venture \cite{MSP14}. However, random sequences generated by Anglican random 
processes are not required to be exchangeable. Random processes are
defined using the \texttt{defproc} macro and implement the
\texttt{anglican.runtime/{\linebreak[0]}random-process} protocol. This
protocol has two methods
\begin{itemize}
\item \texttt{produce}, which returns the distribution on the next
random variable in the sequence, and
\item \texttt{absorb}, which incorporates the value for the next random
variable and returns an updated random process.
\end{itemize}
 As an example, here is a definition of a beta-Bernoulli process, in which
each random variable is distributed according to a Bernoulli distribution with
an unknown parameter that is drawn from a beta distribution:
\begin{lstlisting}[style=default]
(defproc beta-bernoulli
  "beta-Bernoulli process"
  [a b]
  (produce [this] (bernoulli (/ a (+ a b))))
  (absorb [this x]
    (case x
      0 (beta-bernoulli a (inc b))
      1 (beta-bernoulli (inc a) b))))
\end{lstlisting}
Unlike typical implementations of exchangeable random processes,
Anglican's random processes do not have mutable state. The
\texttt{produce} and \texttt{absorb} methods are deterministic
and functional, and therefore do not have corresponding special
forms in Anglican. A sequence of random values can be generated
using a recursive loop in which \texttt{absorb} returns the
updated process for the next iteration. For example:
\begin{lstlisting}[style=default]
(defm sample-beta-binomial [n a b]
  (loop [process (beta-bernoulli a b)
         values []]
    (if (= (count values) n)
      values
      (let [dist (produce process)
            value (sample dist)]
        (recur (absorb process value)
               (conj values value))))))
\end{lstlisting}
Similarly, random processes can also be used to recursively
observe a sequence of values:
\begin{lstlisting}[style=default]
(defm observe-beta-binomial [values a b]
  (loop [process (beta-bernoulli a b)
         values values] 
    (when (not-empty values)
      (let [dist (produce process)
            value (first values)]
        (observe dist value)
        (recur (absorb process value)
               (rest values))))))
\end{lstlisting}

>>>>

In addition to distributions, Anglican provides \textit{random processes},
which define sequences of random variables that are not independent and
identically distributed. Random processes are similar to the so called
`exchangeable random primitives' in Church \cite{GMR+08} and
Venture \cite{MSP14}. However, random sequences generated by Anglican random 
processes are not required to be exchangeable. Random processes are
defined using the \texttt{defproc} macro and implement the
\texttt{anglican.runtime/{\linebreak[0]}random-process} protocol. This
protocol has two methods
\begin{itemize}
\item \texttt{produce}, which returns the distribution on the next
random variable in the sequence, and
\item \texttt{absorb}, which incorporates the value for the next random
variable and returns an updated random process.
\end{itemize}
 As an example, here is a definition of a beta-Bernoulli process, in which
each random variable is distributed according to a Bernoulli distribution with
an unknown parameter that is drawn from a beta distribution:
\begin{lstlisting}[style=default]
(defproc beta-bernoulli
  "beta-Bernoulli process"
  [a b]
  (produce [this] (bernoulli (/ a (+ a b))))
  (absorb [this x]
    (case x
      0 (beta-bernoulli a (inc b))
      1 (beta-bernoulli (inc a) b))))
\end{lstlisting}
Unlike typical implementations of exchangeable random processes,
Anglican's random processes do not have mutable state. The
\texttt{produce} and \texttt{absorb} methods are deterministic
and functional, and therefore do not have corresponding special
forms in Anglican. A sequence of random values can be generated
using a recursive loop in which \texttt{absorb} returns the
updated process for the next iteration. For example:
\begin{lstlisting}[style=default]
(defm sample-beta-binomial [n a b]
  (loop [process (beta-bernoulli a b)
         values []]
    (if (= (count values) n)
      values
      (let [dist (produce process)
            value (sample dist)]
        (recur (absorb process value)
               (conj values value))))))
\end{lstlisting}
Similarly, random processes can also be used to recursively
observe a sequence of values:
\begin{lstlisting}[style=default]
(defm observe-beta-bernoulli [values a b]
  (loop [process (beta-bernoulli a b)
         values values] 
    (when (not-empty values)
      (let [dist (produce process)
            value (first values)]
        (observe dist value)
        (recur (absorb process value)
               (rest values))))))
\end{lstlisting}
